### 2024-02-19 chap_atom_mol/chap_atom_mol.tex
Merge taxonomy paper + Implement Hervé's comments on case_study

\textbf{Disclaimer}: Relying on ``local'' nuclear energy for some (or on importing electrofuels from abroad for others) is highly controversial. On top of purely techno-economic aspects, non-exhaustively mentioned beforehand, there are other ethical, societal or even political considerations to account for when addressing this question. Like the rest of this thesis, the purpose here is only to expose the impact of integrating \gls{SMR} in the Belgian energy landscape, on a strictly techno-economical point of view. This is why, for the sake of transparency, the model and the data are documented and openly available online \cite{readthedocs_pathway} and in the Appendices \ref{app:EnergyScope} and \ref{app:case_study}.

@@

>>>>

\textbf{Disclaimer}: Relying on ``local'' nuclear energy for some (or on importing electrofuels from abroad for others) is highly controversial. On top of purely techno-economic aspects, non-exhaustively mentioned beforehand, there are other ethical, societal or even political considerations to account for when addressing this question. Like the rest of this thesis, the purpose here is only to expose the impact of integrating \gls{SMR} in the Belgian energy landscape, on a strictly techno-economical point of view with a cost-based optimisation. This is why, for the sake of transparency, the model and the data are documented and openly available online \cite{readthedocs_pathway} and in the Appendices \ref{app:EnergyScope} and \ref{app:case_study}.

@@

\section{Discussion}
\label{sec:atom_mol:discuss}

{\color{red} \textbf{Discuss the question of the availability SVB \& CL}}\\
